Msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-28 paper.tex
Add forward simulations section.

@@

Tskit has facilited unprecedented interoperability between simulators:
Forward simulations can also use tree
sequences~\citep{kelleher2018efficient,haller2018tree}. In particular, SLiM
3.0~\citep{haller2019slim} and fwdpp~\citep{thornton2014cpp} can now output
tree sequences. Msprime can take tree sequences simulated by these forward
simulators as input and complete the simulation (``recapitation'').
See \cite{haller2018tree} for more details.

>>>>

\subsection*{Integration with forward simulators}
A unique feature of \msprime\ is its ability to simulate
genetic ancestries conditioned on an existing partial
genetic ancestry. Given a tree sequence that
is complete up until time $t$ as input
(where marginal trees may or may not have fully coalesced),
\msprime\ can efficiently obtain the segments of ancestral material
present at this time, and then run the simulation backwards in time from there.
This allows a simulated ancestry to be produced by any
number of different processes across disjoint time slices.
In practise this feature is used to ``complete''
forwards-time ancestry simulations~\citep{kelleher2018efficient}
that may have not fully coalesced. This process
(``recapitation'') can be orders of magnitude faster than
the standard approach of neutral burn-in; see
\cite{haller2018tree} for more details and examples.
This interoperability between simulators, where a partial ancestry
simulation produced by \SLiM~\citep{haller2019slim}
or \fwdpy~\citep{thornton2014cpp} can be picked up and completed
by another simulator, with complete information
retained---at scale---is unprecedented.

@@
